Forecasting the 2024 U.S. Presidential Election

### 2024-11-04 paper/paper.qmd
Add Reference of Pollster
Add Reference of Pollster

The Marquette Law School Poll employs a rigorous methodology to survey adults in the US on national issues, incorporating probability-based sampling that combines Address-Based Sampling (ABS) and Stratified Random Sampling. This approach, including online and offline respondents, ensures broad representativeness. The SSRS Polling Panel supports participant recruitment, and weighting adjustments enhance result accuracy.

@@

The population for the poll includes adults aged 18 and over across all 50 states and the District of Columbia. The sampling frame was constructed through ABS, leveraging the US Postal Service's Computerized Delivery Sequence (CDS), a comprehensive, regularly updated list of residential addresses. The primary source for participants is the SSRS Opinion Panel, which includes both ABS and telephone survey data to capture hard-to-reach demographics, like non-Internet users. The survey ultimately included 1,005 adults, including registered and likely voters, with weighted samples to ensure proportional representation.

@@

Participants were recruited via the SSRS Omnibus Panel, a probability panel formed from ABS and telephone survey data. This dual approach ensured that both Internet and non-Internet users were included, minimizing online-only bias. Stratified by demographics (age, gender, race, education, region, and partisan affiliation), this process produced a balanced representation across groups. Selected participants received an email invitation with a unique link to the survey. Non-responders received up to two reminder emails, and those who opted for text notifications also received reminders. Participants received an e-gift card incentive upon survey completion.

@@

The Marquette Law School Poll combines ABS and stratified random sampling. The ABS covers all residential addresses using USPS delivery sequences, ensuring broad geographic reach. To include hard-to-reach demographics, SSRS supplements ABS data with telephone survey responses. Stratified sampling by key demographics (age, gender, race, education, region, and political party) ensures representation across major groups. This probability-based sampling minimizes bias but requires significant resources. Stratification and weighting to represent specific populations add to survey complexity and cost.

@@

To address non-response and improve representativeness, SSRS applies weighting adjustments based on demographic variables such as age, gender, race, education, region, and Internet use. This process aligns sample characteristics with adult population parameters, reducing bias from demographic differences in response rates.

@@

The questionnaire is well-designed, with a collaborative approach that reduces respondent burden and improves comprehension. A thoughtfully structured skip pattern enhances flow and minimizes dropout rates. The probability-based sampling, combined with extensive weighting and stratification, enables a representative sample of adults. However, heavy reliance on web-based responses may introduce Internet bias, potentially underrepresenting non-Internet households. Additionally, the questionnaire’s complexity may increase participant fatigue, affecting response completeness. The response rate of approximately 47.4% also indicates some level of attrition in the sample.

>>>>

The Marquette Law School Poll employs a rigorous methodology to survey adults in the US on national issues, incorporating probability-based sampling that combines Address-Based Sampling (ABS) and Stratified Random Sampling [@citemarquette]. This approach, including online and offline respondents, ensures broad representativeness. The SSRS Polling Panel supports participant recruitment, and weighting adjustments enhance result accuracy.

@@

The population for the poll includes adults aged 18 and over across all 50 states and the District of Columbia. The sampling frame was constructed through ABS, leveraging the US Postal Service's Computerized Delivery Sequence (CDS), a comprehensive, regularly updated list of residential addresses. The primary source for participants is the SSRS Opinion Panel, which includes both ABS and telephone survey data to capture hard-to-reach demographics, like non-internet users. The survey ultimately included 1,005 adults, including registered and likely voters, with weighted samples to ensure proportional representation [@citemarquette].

@@

Participants were recruited via the SSRS Omnibus Panel, a probability panel formed from ABS and telephone survey data. This dual approach ensured that both internet and non-internet users were included, minimizing online-only bias. Stratified by demographics (age, gender, race, education, region, and partisan affiliation), this process produced a balanced representation across groups. Selected participants received an email invitation with a unique link to the survey. Non-responders received up to two reminder emails, and those who opted for text notifications also received reminders. Participants received an e-gift card incentive upon survey completion [@citemarquette].

@@

The Marquette Law School Poll combines ABS and stratified random sampling. The ABS covers all residential addresses using USPS delivery sequences, ensuring broad geographic reach. To include hard-to-reach demographics, SSRS supplements ABS data with telephone survey responses. Stratified sampling by key demographics (age, gender, race, education, region, and political party) ensures representation across major groups [@citemarquette]. This probability-based sampling minimizes bias but requires significant resources. Stratification and weighting to represent specific populations add to survey complexity and cost.

@@

To address non-response and improve representativeness, SSRS applies weighting adjustments based on demographic variables such as age, gender, race, education, region, and internet use [@citemarquette]. This process aligns sample characteristics with adult population parameters, reducing bias from demographic differences in response rates.

@@

The questionnaire is well-designed, with a collaborative approach that reduces respondent burden and improves comprehension. A thoughtfully structured skip pattern enhances flow and minimizes dropout rates. The probability-based sampling, combined with extensive weighting and stratification, enables a representative sample of adults. However, heavy reliance on web-based responses may introduce internet bias, potentially underrepresenting non-internet households. Additionally, the questionnaire’s complexity may increase participant fatigue, affecting response completeness. The response rate of approximately 47.4% also indicates some level of attrition in the sample [@citemarquette].
